Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-06-13 output/latex/manuscript.tex
fix reference to supplementary file

Our first experiment attempted to answer whether genes in a disease-relevant LV could represent potential therapeutic targets.
For this, the first step was to obtain a set of genes strongly associated with a phenotype of interest.
Therefore, we performed a fluorescence-based CRISPR-Cas9 in the HepG2 cell line and identified 462 genes associated with lipid regulation (\protect\hyperlink{sec:methods:crispr}{Methods}).
From these, we selected two high-confidence gene sets that either caused a decrease or increase of lipids:
a lipids-decreasing gene-set with eight genes: \emph{BLCAP}, \emph{FBXW7}, \emph{INSIG2}, \emph{PCYT2}, \emph{PTEN}, \emph{SOX9}, \emph{TCF7L2}, \emph{UBE2J2};
and a lipids-increasing gene-set with six genes: \emph{ACACA}, \emph{DGAT2}, \emph{HILPDA}, \emph{MBTPS1}, \emph{SCAP}, \emph{SRPR} (Supplementary File 2).

>>>>

Our first experiment attempted to answer whether genes in a disease-relevant LV could represent potential therapeutic targets.
For this, the first step was to obtain a set of genes strongly associated with a phenotype of interest.
Therefore, we performed a fluorescence-based CRISPR-Cas9 in the HepG2 cell line and identified 462 genes associated with lipid regulation (\protect\hyperlink{sec:methods:crispr}{Methods}).
From these, we selected two high-confidence gene sets that either caused a decrease or increase of lipids:
a lipids-decreasing gene-set with eight genes: \emph{BLCAP}, \emph{FBXW7}, \emph{INSIG2}, \emph{PCYT2}, \emph{PTEN}, \emph{SOX9}, \emph{TCF7L2}, \emph{UBE2J2};
and a lipids-increasing gene-set with six genes: \emph{ACACA}, \emph{DGAT2}, \emph{HILPDA}, \emph{MBTPS1}, \emph{SCAP}, \emph{SRPR} (Supplementary File 1).
